---
title: "Meta-analysis of Liposomal bupivacaine vs others"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile),'/README.md')) })
output: github_document
---
<i> Analysis and visualization developed by [Luis A. Figueroa](https://twitter.com/LuisFig1706) and [Oscar J. Ponce](https://twitter.com/PonceOJ)</i>

The purpose of this site is to make our meta-analysis as transparent as possible. All information or documents used, from the protocol to the final publication, will be available here. If further information is needed, please do not hesitate to contact us.

```{r packages, include=FALSE}
library(metafor)
library(tidyverse)
library(forestplot)
library(rmarkdown)
library(openxlsx)

knitr::opts_chunk$set(fig.path = "Output Figures/", dev='svg') # dev = 'png'
```

```{r cleaning of Dichotomus outcomes, include=FALSE}
data1 <- read.xlsx("Exparel analysis.xlsx", sheet = 2)
data2 <- data1[-c(7,10),]
data2$comp <- c("0.9% sodium chloride","0.9% sodium chloride","","",
                "Bupivacaine HCl 75", "Bupivacaine HCl 75", "","")
data2$n2 <- c("93", "93","","","26","26","","")
data2$e2 <- c("4", "5","","","3","1","","")
names(data2) <- c('Author', 'int', 'n1', 'outc', 'e1','comp','n2','e2')
data2 <- data2[-c(3,4,7,8),]
data2$Author <- c(rep("Gorfine, et. al",2),rep("Haas, et. al",2))
data2$int <- c(rep("LB 300 mg",2),rep("LB 266 mg",2))
data2$n1 <- c(rep("94",2),rep("25",2))
data2 <- data2[,c(1,4,2,6,5,8,3,7)]
rownames(data2) <- NULL
# Convert to numeric variables
data2$e2 <- as.numeric(data2$e2)
data2$n1 <- as.numeric(data2$n1)
data2$n2 <- as.numeric(data2$n2)

# Vomitos
datad_v <- data2[c(1,3),]
# Pain
datad_p <- data2[c(2,4),] 
```

```{r or_dichotomus outcomes_adverse effects, include=FALSE}
dat_v <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_v)
dat_v <- summary(dat_v)
dat_v

dat_p <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_p)
dat_p <- summary(dat_p)
dat_p
```

```{r meta_dichotomus outcomes_adverse effects, include=FALSE}
meta_datv_reml <- rma(yi, vi, method="REML", data=dat_v, test='knha')

meta_datp_reml <- rma(yi, vi, method="REML", data=dat_p, test='knha')
```

```{r predict_dichotomus outcomes_adverse effects, include=FALSE}
meta_v <- predict(meta_datv_reml, transf = exp, digits = 2)

meta_p <- predict(meta_datp_reml, transf = exp, digits = 2)
```

<br>
<h2>Individual Forestplot Dichotomus Data</h2>


<details>

<summary><b>Figure A -</b> Adverse effects of liposomal bupivacaine vs others</summary>
<br>

```{r overall_graph_REML, echo=FALSE, fig.height = 3.8, fig.width = 13.5}
col1f <- c("Author", datad_v$Author, 
      paste("Overall Odds Ratio for", meta_datv_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datv_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datv_reml$parms),
            ", p ", (ifelse(meta_datv_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datv_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datv_reml$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", datad_p$Author, 
      paste("Overall Odds Ratio for", meta_datp_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datp_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datp_reml$parms),
            ", p ", (ifelse(meta_datp_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datp_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datp_reml$I2, digits=1, format="f")), "%)"))

col2f <- c("Liposomal Bupivacaine (n/N)",
      paste(dat_v$e1,"/", dat_v$n1), paste0(sum(dat_v$e1), " / ", sum(dat_v$n1)), NA,
      NA, NA, 
      "Liposomal Bupivacaine (n/N)",
      paste(dat_p$e1,"/", dat_p$n1), paste0(sum(dat_p$e1), " / ", sum(dat_p$n1)), NA)

col3f <- c("others (n/N)",
      paste(dat_v$e2,"/", dat_v$n2), paste0(sum(dat_v$e2), " / ", sum(dat_v$n2)), NA,
      NA, NA,
      "others (n/N)",
      paste(dat_p$e2,"/", dat_p$n2), paste0(sum(dat_p$e2), " / ", sum(dat_p$n2)), NA)

col4f <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_v$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_v$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_v$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_v$pred, format = 'f', digits=2),
            "(", formatC(meta_v$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_v$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_p$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_p$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_p$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_p$pred, format = 'f', digits=2),
            "(", formatC(meta_p$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_p$ci.ub, format = 'f', digits = 2), ")"), NA)

col5f <- c("Weight(%)", paste(formatC(weights(meta_datv_reml), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datp_reml), format='f', digits = 1),'%'), NA, NA)

text1f <- cbind(col1f, col2f, col3f, col4f, col5f)

# Adding subtitles
subtitle1 <- c("Vomiting", rep(NA, 4))
subtitle2 <- c("Pain During Bowel Movements", rep(NA,4))

text1f <- rbind(text1f[1,], subtitle1, text1f[2:6,], subtitle2, text1f[c(9:12),])
rownames(text1f) <- NULL


cf <- structure(list(
          mean = c(rep(NA, 2), exp(dat_v$yi), 2, NA,NA,NA, exp(dat_p$yi), meta_p$pred,NA),
          lower = c(rep(NA, 2), exp(dat_v$ci.lb), 0.1, NA,NA,NA, exp(dat_p$ci.lb), meta_p$ci.lb, NA),
          upper = c(rep(NA, 2), exp(dat_v$ci.ub), 95, NA, NA,NA,exp(dat_p$ci.ub), meta_p$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1f)),
          class = "data.frame")

sizes1f <- c(NA, NA, (weights(meta_datv_reml)*0.01), 1,NA, NA,
             NA, (weights(meta_datp_reml)*0.01), 1, NA)
names(sizes1f) <- NULL

plotf <- forestplot(text1f, 
             graph.pos = 4,
             zero = 1,
             cf,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1f,
             is.summary = c(rep(T, 2), rep(F, 2), T,T,T,T, rep(F, 2), T,T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label = gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = log(c(0.1, 0.5, 1, 4, 15,  95)),
             xlog=T,
             clip = c(0.1, 95),
             grid = c(0.1, 0.5, 4, 15, 95),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotf

```

</details>