---
title: "Meta-analysis of Liposomal bupivacaine vs others"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile),'/README.md')) })
output: github_document
---
<i> Analysis and visualization developed by [Luis A. Figueroa](https://twitter.com/LuisFig1706) and [Oscar J. Ponce](https://twitter.com/PonceOJ)</i>

The purpose of this site is to make our meta-analysis as transparent as possible. All information or documents used, from the protocol to the final publication, will be available here. If further information is needed, please do not hesitate to contact us.

```{r packages, include=FALSE}
library(metafor)
library(tidyverse)
library(forestplot)
library(rmarkdown)
library(openxlsx)

knitr::opts_chunk$set(fig.path = "Cont Output Figures/", dev='svg') # dev = 'png'
```

```{r cleaning of Continous outcome, include=FALSE}
po <- read.xlsx("Pain outcome.xlsx")
od <- read.xlsx("Opiod dose mg.xlsx")
po1 <- po[-c(1,3),-c(6,7,19:22)] # Delete cols that we wont use
od1 <- od[-2,-c(6,7,19:22)] # Delete cols that we wont use

# Renamecols, RefID = Author, Intervention = int, Intervention.Dose = intd, 
# Comparison.(bupivacaine,.placebo,.other) = comp, Comparison.Dose = cd, 
# Total.participants.(n) = tpart, Total.Intervention.(n) = n, Total.comparator(n) = n, 
# SD = sd, IQR = iqr, mean.1 = mean1, SD.1 = sd1, median.1 = median1, IQR.1 = iqr1
names(po1) <- c('Author', 'int', 'intd', 'comp', 'compd', 'tpart', 'n', 'n1', 'mean',
                'sd', 'median', 'iqr', 'mean1', 'sd1', 'median1', 'iqr1')
names(od1) <- c('Author', 'int', 'intd', 'comp', 'compd', 'tpart', 'n', 'n1', 'mean', 
                'sd', 'median', 'iqr', 'mean1', 'sd1', 'median1', 'iqr1')
rownames(po1) <- NULL #Restablecer el numero de filas
rownames(od1) <- NULL #Restablecer el numero de filas

# Dejar variables a una sola unidad
po1$Author[po1$Author == '60'] <- 'Haas, et. al'
po1$Author[po1$Author == '74'] <- 'Kanlıöz, et. al'
po1$intd[po1$intd == '266 mg'] <- '199'
po1$intd[po1$intd == '300 mg'] <- '300'
po1$comp[po1$comp == 'placebo cream'] <- 'placebo'

od1$Author[od1$Author == '58'] <- 'Gorfine, et. al'
od1$Author[od1$Author == '94'] <- 'Shariat, et. al'
od1$intd[od1$intd == '266 mg'] <- '266'
od1$comp[od1$comp == 'placebo (0.9% sodium chloride)'] <- 'placebo'

# convertir a variables numericas
str(po1)
po1$intd <- as.numeric(po1$intd) 
po1$mean <- as.numeric(po1$mean) 
po1$sd <- as.numeric(po1$sd)
po1$mean1 <- as.numeric(po1$mean1) 
po1$sd1 <- as.numeric(po1$sd1)

str(od1)
od1$intd <- as.numeric(od1$intd)
od1$mean <- as.numeric(od1$mean) 
od1$sd <- as.numeric(od1$sd)
od1$mean1 <- as.numeric(od1$mean1) 
od1$sd1 <- as.numeric(od1$sd1)

# Visualizar  si no hay mean & sd, sd & iqr
po1[is.na(po1$mean) & is.na(po1$median),]
po1[is.na(po1$sd) & is.na(po1$iqr),]
po1[is.na(po1$mean1) & is.na(po1$median1),]
po1[is.na(po1$sd1) & is.na(po1$iqr1),]

od1[is.na(od1$mean) & is.na(od1$median),]
od1[is.na(od1$sd) & is.na(od1$iqr),]
od1[is.na(od1$mean1) & is.na(od1$median1),]
od1[is.na(od1$sd1) & is.na(od1$iqr1),]

```


```{r function, echo=FALSE, message=FALSE, warning=FALSE}

table_md <- function(analysis, nstudies, int, comp, outcome, col, 
                     follow=FALSE){
  ifelse(nstudies>1,
        (b <- cbind( 
          c("Author", analysis$pre$Author, 
            paste("Overall Mean Difference for", analysis$ma$k, "studies"),
            paste("(Tau^2 = ", (formatC(analysis$ma$tau2, digits=2, format="f")), ", df = ", 
                  (analysis$ma$k - analysis$ma$p),
                  ", p ", (ifelse(analysis$ma$QEp < 0.001, 
                                  paste("< 0.001"),
                                  paste("= ", formatC(analysis$ma$QEp, digits=3, format="f")))),
                  "; ", "I^2", " = ", (formatC(analysis$ma$I2, digits=1, format="f")), "%)")),
        c(paste(int), analysis$pre$n, sum(analysis$pre$n),NA),
        c(paste(outcome, '\n', col), analysis$pre$postmean1, NA, NA),
        c(paste(comp), analysis$pre$n1,sum(analysis$pre$n1), NA),
        c(paste(outcome, '\n', col), analysis$pre$postmean2, NA, NA),
        c("Mean Difference (95% CI)", analysis$pre$md, 
            paste(formatC(analysis$ma$b, format='f', digits =1), 
                  " (",formatC(analysis$ma$ci.lb, format='f', digits=1),
                  ",", formatC(analysis$ma$ci.ub, format='f', digits=1), ")"), NA),
        c("Weight (%)", analysis$pre$w, NA, NA))),
        (b <- cbind( 
        c("Author", analysis$pre$Author),
        c(paste(int), analysis$pre$n),
        c(paste(outcome,'\n', col), analysis$pre$postmean),
        c(paste(comp), analysis$pre$n1),
        c(paste(outcome, '\n',col), analysis$pre$postmean1),
        c("Mean Difference (95% CI)", analysis$pre$md))))

  ifelse(follow==TRUE, 
          b <- cbind(b, c(paste('Follow-up'), analysis$pre$followup, NA)), NA)
  ifelse(follow==TRUE,
          b <- b[,c(1,ncol(b),2:(ncol(b)-1))], NA)
  
  
  b <- as_tibble(b) 
  b <- b %>% add_row(.before = 2)
  b <- b %>% add_row(.before = 2)
  b <- b %>% add_row(.after = nrow(b))
  
  ifelse(nstudies>1, b <- b %>% add_row(.before = nrow(b)-2), NA)

  
  ifelse(nstudies > 1,
        (c <- structure(list(
          mean = c(rep(NA, 3), analysis$pre$yi, NA, analysis$ma$b,NA, NA),
          lower = c(rep(NA, 3), analysis$pre$ci.lb, NA, analysis$ma$ci.lb, NA, NA),
          upper = c(rep(NA, 3), analysis$pre$ci.ub, NA, analysis$ma$ci.ub, NA, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(b)),
          class = "data.frame")),
        (c <- structure(list(
          mean = c(rep(NA, 3), analysis$pre$yi, NA),
          lower = c(rep(NA, 3), analysis$pre$ci.lb, NA),
          upper = c(rep(NA, 3), analysis$pre$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(b)),
          class = "data.frame")))

  c <- as_tibble(c)
  
  list(b = b, c = c)
} 

```

```{r analysis Pain outcome, echo=FALSE, message=FALSE, warning=FALSE}
db_po <- po1
db_po <- escalc(measure="MD",
             m1i=mean, m2i = mean1, 
             sd1i  = sd, sd2i = sd1, 
             n1i = n, n2i= n1, data=po1)
db_po$vi <- ifelse(is.na(db_po$vi), 
               ((db_po$mdul_post-db1$mdll_post)/((2*abs(qt(0.05/2, db_po$total-1)))^2)), db_po$vi)
db_po <- db_po[order(db_po$yi),]
db_po <- summary(db_po)
  
db_po$md <- paste(formatC(db_po$yi, format='f', digits =1)," ",
               "(",formatC(db_po$ci.lb, format='f', digits =1),
               ",",formatC(db_po$ci.ub, format='f', digits=1),")") 
db_po$postmean1 <- paste(formatC(db_po$mean, format='f', digits=1),'(', formatC(db_po$sd, format='f', digits=1),')')
db_po$postmean2 <- paste(formatC(db_po$mean1, format='f', digits=1),'(', formatC(db_po$sd1, format='f', digits=1),')')
  
ma_po <- rma(yi, vi, measure='MD', data=db_po, method='REML', test = 'knha')
finpo <- predict(ma_po)

db_po$w <- paste(formatC(weights(ma_po), format='f', digits = 1),'%')
db_po$weights <- weights(ma_po)
  
pof <- list(pre = db_po, ma = ma_po)

# Primera function que no pude entender
tbl_md_po <- table_md(analysis = pof, nstudies = 2, 
                    int = "Liposomal bupivacaine (n)", comp = "Others (n)",
                    outcome = 'Pain (NRS)', col = 'Mean (SD)', 
                  follow = FALSE)


db_od <- od1
db_od <- escalc(measure="SMD", 
             m1i=mean, m2i = mean1, 
             sd1i  = sd, sd2i = sd1, 
             n1i = n, n2i= n1, data=od1)

db_od <- db_od[order(db_od$yi),]
db_od <- summary(db_od)
  
db_od$md <- paste(formatC(db_od$yi, format='f', digits =1)," ",
               "(",formatC(db_od$ci.lb, format='f', digits =1),
               ",",formatC(db_od$ci.ub, format='f', digits=1),")") 
db_od$postmean1 <- paste(formatC(db_od$mean, format='f', digits=1),'(', formatC(db_od$sd, format='f', digits=1),')')
db_od$postmean2 <- paste(formatC(db_od$mean1, format='f', digits=1),'(', formatC(db_od$sd1, format='f', digits=1),')')
  
ma_od <- rma(yi, vi, measure='SMD', data=db_od, method='REML')
finod <- predict(ma_od)

db_od$w <- paste(formatC(weights(ma_od), format='f', digits = 1),'%')
db_od$weights <- weights(ma_od)
  
odf <- list(pre = db_od, ma = ma_od)

# Primera function que no pude entender
tbl_md_od <- table_md(analysis = odf, nstudies = 2, 
                    int = "Liposomal bupivacaine (n)", comp = "Placebo (n)",
                    outcome = 'Dose of opiod rescue medication (mg)', col = 'Mean (SD)', 
                  follow = FALSE)
```

<h2>Individual Forestplots Continuous Data</h2>

<details>

<summary><b>Figure A -</b> Pain Outcome with liposomal bupivacaine vs others </summary>
<br>

```{r cont_graphs po, echo=FALSE, fig.height = 2.2, fig.width = 15}
title1 <- c('', paste0('Liposomal bupivacaine (n)'), "mean (SD)",
            paste0('Others'), "mean (SD)",
            paste0('Mean Difference (MD) 95%CI'), 
            paste0('Weights'))

sub_cont1 <- c('Pain (NRS)', rep(NA, 6))

subtotal1 <- rbind(title1, NA,
                   sub_cont1, tbl_md_po$b[-c(1:3, nrow(tbl_md_po$b)-3),])
subtotal1 <- as.matrix(subtotal1)

subtotal1_summary <- c(T, F, 
                       T, rep(F, nrow(tbl_md_po$b[-c(1:3, nrow(tbl_md_po$b)-3),])-3),T,T,F)

sizes_cont1 <- c(rep(NA,3), 0.005*(pof$pre$weights),1,
                rep(NA, 2))

subtotal1n <- rbind(NA,NA,
                    NA, tbl_md_po$c[-c(1:3, nrow(tbl_md_po$c)-3),])

plot1 <- forestplot(subtotal1,
             graph.pos = 6,
             zero = 0,
             subtotal1n,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:8, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes_cont1,
             line.margin = 2,
             is.summary = subtotal1_summary,
             align = c('l', rep('c', 4), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(-15,0,12),
             xlog=FALSE,
             clip = c(-15,12),
             grid = c(-15,0,12),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(8,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))

plot1
```


</details>



<details>

<summary><b>Figure B -</b> Dose of rescue medication Outcome with liposomal bupivacaine vs placebo </summary>
<br>


```{r cont_graphs od, echo=FALSE, fig.height = 2.2, fig.width = 15}
title2 <- c('', paste0('Liposomal bupivacaine (n)'), "mean (SD)",
            paste0('Placebo'), "mean (SD)",
            paste0('Mean Difference (SMD) 95%CI'), 
            paste0('Weights'))

sub_cont2 <- c('Dose of opiod rescue medication (mg)', rep(NA, 6))

subtotal2 <- rbind(title2, NA,
                   sub_cont2, tbl_md_od$b[-c(1:3, nrow(tbl_md_od$b)-3),])
subtotal2 <- as.matrix(subtotal2)

subtotal2_summary <- c(T, F, 
                       T, rep(F, nrow(tbl_md_od$b[-c(1:3, nrow(tbl_md_od$b)-3),])-3), T, T,F)

sizes_cont2 <- c(rep(NA,3), 0.005*(odf$pre$weights),1,
                rep(NA, 2))

subtotal2n <- rbind(NA,NA,
                    NA, tbl_md_od$c[-c(1:3, nrow(tbl_md_od$c)-3),])

plot2 <- forestplot(subtotal2,
             graph.pos = 6,
             zero = 0,
             subtotal2n,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:8, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes_cont2,
             line.margin = 2,
             is.summary = subtotal2_summary,
             align = c('l', rep('c', 4), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(-2,0,2),
             xlog=FALSE,
             clip = c(-1.5,2),
             grid = c(-1.5,0,2),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(8,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))

plot2
```

</details>
