---
title: "Meta-analysis of Liposomal bupivacaine vs others"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile),'/README.md')) })
output: github_document
---
<i> Analysis and visualization developed by [Luis A. Figueroa](https://twitter.com/LuisFig1706) and [Oscar J. Ponce](https://twitter.com/PonceOJ)</i>

The purpose of this site is to make our meta-analysis as transparent as possible. All information or documents used, from the protocol to the final publication, will be available here. If further information is needed, please do not hesitate to contact us.

```{r packages, include=FALSE}
library(metafor)
library(tidyverse)
library(forestplot)
library(rmarkdown)
library(openxlsx)

knitr::opts_chunk$set(fig.path = "Cont Output Figures/", dev='svg') # dev = 'png'
```

```{r function, echo=FALSE, message=FALSE, warning=FALSE}

table_md <- function(analysis, nstudies, int, comp, outcome, col, 
                     follow=FALSE){
  ifelse(nstudies>1,
        (b <- cbind( 
          c("Author", analysis$pre$Author, 
            paste("Overall Mean Difference for", analysis$ma$k, "studies"),
            paste("(Tau^2 = ", (formatC(analysis$ma$tau2, digits=2, format="f")), ", df = ", 
                  (analysis$ma$k - analysis$ma$p),
                  ", p ", (ifelse(analysis$ma$QEp < 0.001, 
                                  paste("< 0.001"),
                                  paste("= ", formatC(analysis$ma$QEp, digits=3, format="f")))),
                  "; ", "I^2", " = ", (formatC(analysis$ma$I2, digits=1, format="f")), "%)")),
        c(paste(int), analysis$pre$n, sum(analysis$pre$n),NA),
        c(paste(outcome, '\n', col), analysis$pre$postmean1, NA, NA),
        c(paste(comp), analysis$pre$n1,sum(analysis$pre$n1), NA),
        c(paste(outcome, '\n', col), analysis$pre$postmean2, NA, NA),
        c("Mean Difference (95% CI)", analysis$pre$md, 
            paste(formatC(analysis$ma$b, format='f', digits =1), 
                  " (",formatC(analysis$ma$ci.lb, format='f', digits=1),
                  ",", formatC(analysis$ma$ci.ub, format='f', digits=1), ")"), NA),
        c("Weight (%)", analysis$pre$w, NA, NA))),
        (b <- cbind( 
        c("Author", analysis$pre$Author),
        c(paste(int), analysis$pre$n),
        c(paste(outcome,'\n', col), analysis$pre$postmean),
        c(paste(comp), analysis$pre$n1),
        c(paste(outcome, '\n',col), analysis$pre$postmean1),
        c("Mean Difference (95% CI)", analysis$pre$md))))

  ifelse(follow==TRUE, 
          b <- cbind(b, c(paste('Follow-up'), analysis$pre$followup, NA)), NA)
  ifelse(follow==TRUE,
          b <- b[,c(1,ncol(b),2:(ncol(b)-1))], NA)
  
  
  b <- as_tibble(b) 
  b <- b %>% add_row(.before = 2)
  b <- b %>% add_row(.before = 2)
  b <- b %>% add_row(.after = nrow(b))
  
  ifelse(nstudies>1, b <- b %>% add_row(.before = nrow(b)-2), NA)

  
  ifelse(nstudies > 1,
        (c <- structure(list(
          mean = c(rep(NA, 3), analysis$pre$yi, NA, analysis$ma$b,NA, NA),
          lower = c(rep(NA, 3), analysis$pre$ci.lb, NA, analysis$ma$ci.lb, NA, NA),
          upper = c(rep(NA, 3), analysis$pre$ci.ub, NA, analysis$ma$ci.ub, NA, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(b)),
          class = "data.frame")),
        (c <- structure(list(
          mean = c(rep(NA, 3), analysis$pre$yi, NA),
          lower = c(rep(NA, 3), analysis$pre$ci.lb, NA),
          upper = c(rep(NA, 3), analysis$pre$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(b)),
          class = "data.frame")))

  c <- as_tibble(c)
  
  list(b = b, c = c)
} 

```

```{r cleaning of Dichotomus outcomes, include=FALSE}
data2 <- read.xlsx("Data extraction cleaned.xlsx", sheet = 4)
View(data2)

# Eliminamos los que tenian pre-operatorio diferente y datos no dicotomicos
colnames(data2)
dic1 <- data2[-c(1,2,36,38,40), -c(7,12,14,15,16,17,18)] 
rownames(dic1) <- NULL

# Renamecols, RefID = id, Intervention = int, Intervention.Dose = intd, 
# Comparison = comp, Comparison.Dose = cd, Outcomes:.adverse.effects = outc, 
# Total.participants.(n) = tpart, Total.Intervention.(n) = n1, 
# Total.comparator(n) = n2, n = e1, n = e2
names(dic1) <- c('id', 'int', 'intd', 'comp', 'compd', 'outc', 'tpart', 'n1', 
                  'n2', 'e1', 'e2')

# Complete total participants with tint + tcomp
dic1$tpart <- dic1$n1 + dic1$n2

# Dosis de intervencion en una sola unidad
table(dic1$intd)
dic1$intd[dic1$intd == '199 mg'] <- '199'
dic1$intd[dic1$intd == '266 mg'] <- '266'
dic1$intd[dic1$intd == '300 mg'] <- '300'
dic1$intd[dic1$intd == '66 mg'] <- '66'
table(dic1$intd)

# Fusionar distintos placebo como un unico placebo general
table(dic1$comp) # Preguntar si ponemos como multimodal al lb + aloe vera
dic1$comp[dic1$comp == 'placebo cream'] <- 'placebo'
dic1$comp[dic1$comp == 'placebo (0.9% sodium chloride)'] <- 'placebo'
table(dic1$comp)

# Convert to numeric variables
str(dic1)
dic1$intd <- as.numeric(dic1$intd)
dic1$e1 <- as.numeric(dic1$e1)
dic1$e2 <- as.numeric(dic1$e2)
str(dic1)

# Solo inclkuir un estudio de cada ID, primera eleccion el que tenga más tpart
# Luego se hará un análisis de sensibilidad y no se harán

# Mas de dos efectos adversos <- Patients with _x0002_1 AEa 
datad_2ae <- dic1[c(1,15),] # 8, 22 <- otros estudios
datad_2ae$Author <- c("Gorfine, et. al", "Haas, et. al")
datad_2ae

# Nausea/vomitos  <- agrupar outcomes
datad_vn <- dic1[c(25, 29, 5), ] # 11, 18, 25, 31, 12, 37, 26, 19
datad_vn$Author <- c("Haas, et. al", "Shariat, et. al", "Gorfine, et. al")
datad_vn

# Pain <- Include: Painful defecation, Pain
datad_p <- dic1[c(4,30), ] # 32
datad_p$Author <- c("Gorfine, et. al", "Shariat, et. al")
datad_p

# Anal hemorragy <- Include Anal hemorragy and Rectal hemorrhage
datad_ah <- dic1[c(3,28), ] # 7, 21, 14
datad_ah$Author <- c("Gorfine, et. al", "Haas, et. al")
datad_ah

# datad_ah1 <- dic1[c(7,21), ] # 3, 14, 28 ANALISIS SENSIBILIDAD
# datad_ah1 # NO se hace porque dosis es dijerente

# Gastrointestinal AEs 
datad_ga <- dic1[c(2,16), ] # 9, 23
datad_ga$Author <- c("Gorfine, et. al", "Haas, et. al")
datad_ga

#Flatulence 
# datad_f <- dic1[c(13,20,27), ] #NO SE PUEDE ANALIZAR PORQUE SON MISMO ID

# Analgesic rescue medication 12h post + Need aditional narcaotic in PACU
# Ya no se analiza porque un estudio es solo Abstract
# datad_rm <- dic1[c(33, 36), ] #34, 35
# datad_rm$Author <- c("GorfineKanlıöz, et. al", "Finucan, et. al")
# datad_rm
```

```{r cleaning of Continous outcome, include=FALSE}
po <- read.xlsx("Pain outcome.xlsx")
od <- read.xlsx("Opiod dose mg.xlsx")
po1 <- po[-c(1,3),-c(6,7,19:22)] # Delete cols that we wont use
od1 <- od[-2,-c(6,7,19:22)] # Delete cols that we wont use

# Renamecols, RefID = Author, Intervention = int, Intervention.Dose = intd, 
# Comparison.(bupivacaine,.placebo,.other) = comp, Comparison.Dose = cd, 
# Total.participants.(n) = tpart, Total.Intervention.(n) = n, Total.comparator(n) = n, 
# SD = sd, IQR = iqr, mean.1 = mean1, SD.1 = sd1, median.1 = median1, IQR.1 = iqr1
names(po1) <- c('Author', 'int', 'intd', 'comp', 'compd', 'tpart', 'n', 'n1', 'mean',
                'sd', 'median', 'iqr', 'mean1', 'sd1', 'median1', 'iqr1')
names(od1) <- c('Author', 'int', 'intd', 'comp', 'compd', 'tpart', 'n', 'n1', 'mean', 
                'sd', 'median', 'iqr', 'mean1', 'sd1', 'median1', 'iqr1')
rownames(po1) <- NULL #Restablecer el numero de filas
rownames(od1) <- NULL #Restablecer el numero de filas

# Dejar variables a una sola unidad
po1$Author[po1$Author == '60'] <- 'Haas, et. al'
po1$Author[po1$Author == '74'] <- 'Kanlıöz, et. al'
po1$intd[po1$intd == '266 mg'] <- '199'
po1$intd[po1$intd == '300 mg'] <- '300'
po1$comp[po1$comp == 'placebo cream'] <- 'placebo'

od1$Author[od1$Author == '58'] <- 'Gorfine, et. al'
od1$Author[od1$Author == '94'] <- 'Shariat, et. al'
od1$intd[od1$intd == '266 mg'] <- '266'
od1$comp[od1$comp == 'placebo (0.9% sodium chloride)'] <- 'placebo'

# convertir a variables numericas
str(po1)
po1$intd <- as.numeric(po1$intd) 
po1$mean <- as.numeric(po1$mean) 
po1$sd <- as.numeric(po1$sd)
po1$mean1 <- as.numeric(po1$mean1) 
po1$sd1 <- as.numeric(po1$sd1)

str(od1)
od1$intd <- as.numeric(od1$intd)
od1$mean <- as.numeric(od1$mean) 
od1$sd <- as.numeric(od1$sd)
od1$mean1 <- as.numeric(od1$mean1) 
od1$sd1 <- as.numeric(od1$sd1)

# Visualizar  si no hay mean & sd, sd & iqr
po1[is.na(po1$mean) & is.na(po1$median),]
po1[is.na(po1$sd) & is.na(po1$iqr),]
po1[is.na(po1$mean1) & is.na(po1$median1),]
po1[is.na(po1$sd1) & is.na(po1$iqr1),]

od1[is.na(od1$mean) & is.na(od1$median),]
od1[is.na(od1$sd) & is.na(od1$iqr),]
od1[is.na(od1$mean1) & is.na(od1$median1),]
od1[is.na(od1$sd1) & is.na(od1$iqr1),]

```

```{r or_dichotomus outcomes_adverse effects, include=FALSE}
dat_2ae <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_2ae)
dat_2ae <- summary(dat_2ae)
dat_2ae

dat_vn <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_vn)
dat_vn <- summary(dat_vn)
dat_vn

dat_p <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_p)
dat_p <- summary(dat_p)
dat_p

dat_ah <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_ah)
dat_ah <- summary(dat_ah)
dat_ah

#dat_ah1 <- escalc(measure="OR", ai=n1, bi=n2,
#              ci=e1, di=e2, data=datad_ah1) #ANALISIS SENSIBILIDAD
#dat_ah1 <- summary(dat_ah1)
#dat_ah1


dat_ga <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=datad_ga)
dat_ga <- summary(dat_ga)
dat_ga

# at_f <- escalc(measure="OR", ai=n1, bi=n2,
#              ci=e1, di=e2, data=datad_f)
# dat_f <- summary(dat_f)
# dat_f

# dat_rm <- escalc(measure="OR", ai=n1, bi=n2,
#              ci=e1, di=e2, data=datad_rm)
# dat_rm <- summary(dat_rm)
# dat_rm
```

```{r meta_dichotomus outcomes_adverse effects, include=FALSE}
meta_dat2ae_reml <- rma(yi, vi, method="REML", data=dat_2ae, test='knha')
meta_dat2ae_reml

meta_datvn_reml <- rma(yi, vi, method="REML", data=dat_vn, test='knha')
meta_datvn_reml

meta_datp_reml <- rma(yi, vi, method="REML", data=dat_p, test='knha')
meta_datp_reml

meta_datah_reml <- rma(yi, vi, method="REML", data=dat_ah, test='knha')
meta_datah_reml

#meta_datah1_reml <- rma(yi, vi, method="REML", data=dat_ah1, test='knha') #ANALISIS SENSIBILIDAD
#meta_datah1_reml 

meta_datga_reml <- rma(yi, vi, method="REML", data=dat_ga, test='knha')
meta_datga_reml

# meta_datf_reml <- rma(yi, vi, method="REML", data=dat_f, test='knha')
# meta_datf_reml

# meta_datrm_reml <- rma(yi, vi, method="REML", data=dat_rm, test='knha')
# meta_datrm_reml
```

```{r predict_dichotomus outcomes_adverse effects, include=FALSE}
meta_2ae <- predict(meta_dat2ae_reml, transf = exp, digits = 2)
meta_2ae

meta_vn <- predict(meta_datvn_reml, transf = exp, digits = 2)
meta_vn

meta_p <- predict(meta_datp_reml, transf = exp, digits = 2)
meta_p

meta_ah <- predict(meta_datah_reml, transf = exp, digits = 2)
meta_ah

#meta_ah1 <- predict(meta_datah1_reml, transf = exp, digits = 2) #ANALISIS SENSIBILIDAD 
#meta_ah

meta_ga <- predict(meta_datga_reml, transf = exp, digits = 2)
meta_ga

#meta_f <- predict(meta_datf_reml, transf = exp, digits = 2)
#meta_f

# meta_rm <- predict(meta_datrm_reml, transf = exp, digits = 2) 
# meta_rm
```

```{r analysis continuous, echo=FALSE, message=FALSE, warning=FALSE}
db_po <- po1
db_po <- escalc(measure="MD",
             m1i=mean, m2i = mean1, 
             sd1i  = sd, sd2i = sd1, 
             n1i = n, n2i= n1, data=po1)
db_po$vi <- ifelse(is.na(db_po$vi), 
               ((db_po$mdul_post-db1$mdll_post)/((2*abs(qt(0.05/2, db_po$total-1)))^2)), db_po$vi)
db_po <- db_po[order(db_po$yi),]
db_po <- summary(db_po)
  
db_po$md <- paste(formatC(db_po$yi, format='f', digits =1)," ",
               "(",formatC(db_po$ci.lb, format='f', digits =1),
               ",",formatC(db_po$ci.ub, format='f', digits=1),")") 
db_po$postmean1 <- paste(formatC(db_po$mean, format='f', digits=1),'(', formatC(db_po$sd, format='f', digits=1),')')
db_po$postmean2 <- paste(formatC(db_po$mean1, format='f', digits=1),'(', formatC(db_po$sd1, format='f', digits=1),')')
  
ma_po <- rma(yi, vi, measure='MD', data=db_po, method='REML', test = 'knha')
finpo <- predict(ma_po)

db_po$w <- paste(formatC(weights(ma_po), format='f', digits = 1),'%')
db_po$weights <- weights(ma_po)
  
pof <- list(pre = db_po, ma = ma_po)

# Primera function que no pude entender
tbl_md_po <- table_md(analysis = pof, nstudies = 2, 
                    int = "Liposomal bupivacaine (n)", comp = "Others (n)",
                    outcome = 'Pain (NRS)', col = 'Mean (SD)', 
                  follow = FALSE)


db_od <- od1
db_od <- escalc(measure="SMD", 
             m1i=mean, m2i = mean1, 
             sd1i  = sd, sd2i = sd1, 
             n1i = n, n2i= n1, data=od1)

db_od <- db_od[order(db_od$yi),]
db_od <- summary(db_od)
  
db_od$md <- paste(formatC(db_od$yi, format='f', digits =1)," ",
               "(",formatC(db_od$ci.lb, format='f', digits =1),
               ",",formatC(db_od$ci.ub, format='f', digits=1),")") 
db_od$postmean1 <- paste(formatC(db_od$mean, format='f', digits=1),'(', formatC(db_od$sd, format='f', digits=1),')')
db_od$postmean2 <- paste(formatC(db_od$mean1, format='f', digits=1),'(', formatC(db_od$sd1, format='f', digits=1),')')
  
ma_od <- rma(yi, vi, measure='SMD', data=db_od, method='REML')
finod <- predict(ma_od)

db_od$w <- paste(formatC(weights(ma_od), format='f', digits = 1),'%')
db_od$weights <- weights(ma_od)
  
odf <- list(pre = db_od, ma = ma_od)

# Primera function que no pude entender
tbl_md_od <- table_md(analysis = odf, nstudies = 2, 
                    int = "Liposomal bupivacaine (n)", comp = "Placebo (n)",
                    outcome = 'Dose of opiod rescue medication (mg)', col = 'Mean (SD)', 
                  follow = FALSE)
```

<br>
<h2>Individual Forestplots Dichotomus Data</h2>


<details>

<summary><b>Figure A -</b> Adverse effects of liposomal bupivacaine vs others</summary>
<br>

```{r overall_graph_REML, echo=FALSE, fig.height = 9.8, fig.width = 13.5}
col1f <- c("Author", datad_2ae$Author, 
      paste("Overall Odds Ratio for", meta_dat2ae_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_dat2ae_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_dat2ae_reml$parms),
            ", p ", (ifelse(meta_dat2ae_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_dat2ae_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_dat2ae_reml$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", datad_vn$Author, 
      paste("Overall Odds Ratio for", meta_datvn_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datvn_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datvn_reml$parms),
            ", p ", (ifelse(meta_datvn_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datvn_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datvn_reml$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", datad_p$Author, 
      paste("Overall Odds Ratio for", meta_datp_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datp_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datp_reml$parms),
            ", p ", (ifelse(meta_datp_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datp_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datp_reml$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", datad_ah$Author, 
      paste("Overall Odds Ratio for", meta_datah_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datah_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datah_reml$parms),
            ", p ", (ifelse(meta_datah_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datah_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datah_reml$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", datad_ga$Author, 
      paste("Overall Odds Ratio for", meta_datga_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datga_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datga_reml$parms),
            ", p ", (ifelse(meta_datga_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datga_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datga_reml$I2, digits=1, format="f")), "%)"))

col2f <- c("Liposomal Bupivacaine (n/N)",
      paste(dat_2ae$e1,"/", dat_2ae$n1), paste0(sum(dat_2ae$e1), " / ", sum(dat_2ae$n1)), NA, 
      NA, NA,
      "Liposomal Bupivacaine (n/N)",
      paste(dat_vn$e1,"/", dat_vn$n1), paste0(sum(dat_vn$e1), " / ", sum(dat_vn$n1)), NA,
      NA, NA, 
      "Liposomal Bupivacaine (n/N)",
      paste(dat_p$e1,"/", dat_p$n1), paste0(sum(dat_p$e1), " / ", sum(dat_p$n1)), NA,
      NA, NA, 
      "Liposomal Bupivacaine (n/N)",
      paste(dat_ah$e1,"/", dat_ah$n1), paste0(sum(dat_ah$e1), " / ", sum(dat_ah$n1)), NA,
      NA, NA, 
      "Liposomal Bupivacaine (n/N)",
      paste(dat_ga$e1,"/", dat_ga$n1), paste0(sum(dat_ga$e1), " / ", sum(dat_ga$n1)), NA)

col3f <- c("others (n/N)",
      paste(dat_2ae$e2,"/", dat_2ae$n2), paste0(sum(dat_2ae$e2), " / ", sum(dat_2ae$n2)), NA,
      NA, NA,
      "others (n/N)",
      paste(dat_vn$e2,"/", dat_vn$n2), paste0(sum(dat_vn$e2), " / ", sum(dat_vn$n2)), NA,
      NA, NA,
      "others (n/N)",
      paste(dat_p$e2,"/", dat_p$n2), paste0(sum(dat_p$e2), " / ", sum(dat_p$n2)), NA,
      NA, NA,
      "others (n/N)",
      paste(dat_ah$e2,"/", dat_ah$n2), paste0(sum(dat_ah$e2), " / ", sum(dat_ah$n2)), NA,
      NA, NA,
      "others (n/N)",
      paste(dat_ga$e2,"/", dat_ga$n2), paste0(sum(dat_ga$e2), " / ", sum(dat_ga$n2)), NA)


col4f <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_2ae$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_2ae$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_2ae$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_2ae$pred, format = 'f', digits=2),
            "(", formatC(meta_2ae$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_2ae$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_vn$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_vn$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_vn$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_vn$pred, format = 'f', digits=2),
            "(", formatC(meta_vn$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_vn$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_p$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_p$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_p$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_p$pred, format = 'f', digits=2),
            "(", formatC(meta_p$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_p$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_ah$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_ah$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_ah$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_ah$pred, format = 'f', digits=2),
            "(", formatC(meta_ah$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_ah$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_ga$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_ga$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_ga$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_ga$pred, format = 'f', digits=2),
            "(", formatC(meta_ga$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_ga$ci.ub, format = 'f', digits = 2), ")"), NA)

col5f <- c("Weight(%)", paste(formatC(weights(meta_dat2ae_reml), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datvn_reml), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datp_reml), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datah_reml), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datga_reml), format='f', digits = 1),'%'), NA, NA)

text1f <- cbind(col1f, col2f, col3f, col4f, col5f)


# Adding subtitles
subtitle1 <- c("More than 2 side effects", rep(NA,4))
subtitle2 <- c("Nausea and vomites ", rep(NA, 4))
subtitle3 <- c("Pain", rep(NA,4))
subtitle4 <- c("Anal bleeding", rep(NA,4))
subtitle5 <- c("Gastrointestinal AEs", rep(NA,4))

text1f <- rbind(text1f[1,], subtitle1, text1f[2:7,], subtitle2, text1f[c(9:15),],
                subtitle3, text1f[c(17:22),], subtitle4, text1f[c(24:29),],
                subtitle5, text1f[c(31:34),])
rownames(text1f) <- NULL


cf <- structure(list(
          mean = c(rep(NA, 2), exp(dat_2ae$yi), meta_2ae$pred, rep(NA, 4), exp(dat_vn$yi), meta_vn$pred, rep(NA, 4), exp(dat_p$yi), meta_p$pred, rep(NA, 4), exp(dat_ah$yi), meta_ah$pred, rep(NA, 4), exp(dat_ga$yi), meta_ga$pred,NA),
          lower = c(rep(NA, 2), exp(dat_2ae$ci.lb), meta_2ae$ci.lb, rep(NA, 4), exp(dat_vn$ci.lb), meta_vn$ci.lb, rep(NA, 4), exp(dat_p$ci.lb), meta_p$ci.lb, rep(NA, 4), exp(dat_ah$ci.lb), meta_ah$ci.lb, rep(NA, 4), exp(dat_ga$ci.lb), meta_ga$ci.lb, NA),
          upper = c(rep(NA, 2), exp(dat_2ae$ci.ub), meta_2ae$ci.ub, rep(NA, 4), exp(dat_vn$ci.ub), meta_vn$ci.ub, rep(NA, 4), exp(dat_p$ci.ub), meta_p$ci.ub, rep(NA, 4), exp(dat_ah$ci.ub), meta_ah$ci.ub, rep(NA, 4), exp(dat_ga$ci.ub), meta_ga$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1f)),
          class = "data.frame")

sizes1f <- c(NA, NA, (weights(meta_dat2ae_reml)*0.014), 1, rep(NA, 3),
             NA, (weights(meta_datvn_reml)*0.012), 1, rep(NA, 3), 
             NA, (weights(meta_datp_reml)*0.016), 1, rep(NA, 3),
             NA, (weights(meta_datah_reml)*0.018), 1, rep(NA, 3),
             NA, (weights(meta_datga_reml)*0.014), 1, NA)
names(sizes1f) <- NULL

plotf <- forestplot(text1f, 
             graph.pos = 4,
             zero = 1,
             cf,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1f,
             is.summary = c(rep(T, 2), rep(F, 2), rep(T, 5), rep(F, 3), rep(T, 5),
                            rep(F, 2), rep(T, 5), rep(F,2), rep(T, 5), rep(F,2),
                            T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label = gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.025, 0.01, 1, 4, 15,  95),
             xlog=TRUE,
             clip = c(0.025, 95),
             grid = c(0.025, 0.1,  4, 15, 95),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotf

```

</details>


<h2>Individual Forestplots Continuous Data</h2>

<details>

<summary><b>Figure B -</b> Pain Outcome with liposomal bupivacaine vs others </summary>
<br>

```{r cont_graphs po, echo=FALSE, fig.height = 2.2, fig.width = 15}
title1 <- c('', paste0('Liposomal bupivacaine (n)'), "mean (SD)",
            paste0('Others'), "mean (SD)",
            paste0('Mean Difference (MD) 95%CI'), 
            paste0('Weights'))

sub_cont1 <- c('Pain (NRS)', rep(NA, 6))

subtotal1 <- rbind(title1, NA,
                   sub_cont1, tbl_md_po$b[-c(1:3, nrow(tbl_md_po$b)-3),])
subtotal1 <- as.matrix(subtotal1)

subtotal1_summary <- c(T, F, 
                       T, rep(F, nrow(tbl_md_po$b[-c(1:3, nrow(tbl_md_po$b)-3),])-3),T,T,F)

sizes_cont1 <- c(rep(NA,3), 0.005*(pof$pre$weights),1,
                rep(NA, 2))

subtotal1n <- rbind(NA,NA,
                    NA, tbl_md_po$c[-c(1:3, nrow(tbl_md_po$c)-3),])

plot1 <- forestplot(subtotal1,
             graph.pos = 6,
             zero = 0,
             subtotal1n,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:8, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes_cont1,
             line.margin = 2,
             is.summary = subtotal1_summary,
             align = c('l', rep('c', 4), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(-15,0,12),
             xlog=FALSE,
             clip = c(-15,12),
             grid = c(-15,0,12),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(8,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))

plot1
```


</details>



<details>

<summary><b>Figure C -</b> Dose of rescue medication Outcome with liposomal bupivacaine vs placebo </summary>
<br>


```{r cont_graphs od, echo=FALSE, fig.height = 2.2, fig.width = 15}
title2 <- c('', paste0('Liposomal bupivacaine (n)'), "mean (SD)",
            paste0('Placebo'), "mean (SD)",
            paste0('Mean Difference (SMD) 95%CI'), 
            paste0('Weights'))

sub_cont2 <- c('Dose of opiod rescue medication (mg)', rep(NA, 6))

subtotal2 <- rbind(title2, NA,
                   sub_cont2, tbl_md_od$b[-c(1:3, nrow(tbl_md_od$b)-3),])
subtotal2 <- as.matrix(subtotal2)

subtotal2_summary <- c(T, F, 
                       T, rep(F, nrow(tbl_md_od$b[-c(1:3, nrow(tbl_md_od$b)-3),])-3), T, T,F)

sizes_cont2 <- c(rep(NA,3), 0.005*(odf$pre$weights),1,
                rep(NA, 2))

subtotal2n <- rbind(NA,NA,
                    NA, tbl_md_od$c[-c(1:3, nrow(tbl_md_od$c)-3),])

plot2 <- forestplot(subtotal2,
             graph.pos = 6,
             zero = 0,
             subtotal2n,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:8, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes_cont2,
             line.margin = 2,
             is.summary = subtotal2_summary,
             align = c('l', rep('c', 4), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(-2,0,2),
             xlog=FALSE,
             clip = c(-1.5,2),
             grid = c(-1.5,0,2),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(8,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))

plot2
```

</details>